Need a good title.

### 2018-02-14 ms.tex
fixed formulas in the ms

The typical phylogenetic regression is of the form:
\begin{align}
y & = XB + \epsilon \\
\epsilon & \sim MVN(0,\sigma^{2}C),
\label{eq:gls}
\end{align}
where $y$ is an $n \times 1$ vector of measureable response phenotypic trait; $X$ is an $n \times (m + 1)$ model matrix containing 1's in the first column and the $m$ independment variable (traits); $B$ is an $m + 1$ coefficient vector; $\espilon$ is the residual error and assumed to be multivariate normally distributed with a variance-covariance matrix given by $\sigma^{2}_{ \epsilon} C$ in which $C$ is an $n \times n$ matrix of the phylogenetic correlation (PC).

@@

\begin{align}
Z^{C} & = BS Z ,
\end{align}

where $BS$ is an $b \times s$ matrix of branch--species relation.

\ml{for correlated intercept and slope it is $Z^{C} = Kron(BS,diag(repterm))^T * Z$}

@@

We generate test data using a simple glmm framework that varies in complexity in random effect. All simulations and fits were performed with R.

>>>>

The typical phylogenetic regression is of the form:
\begin{align}
y & = XB + \epsilon \\
\epsilon & \sim MVN(0,\sigma^{2}C),
\label{eq:gls}
\end{align}
where $y$ is an $n \times 1$ vector of measureable response phenotypic trait; $X$ is an $n \times (m + 1)$ model matrix containing 1's in the first column and the $m$ independment variable (traits); $B$ is an $m + 1$ coefficient vector; $\epsilon$ is the residual error and assumed to be multivariate normally distributed with a variance-covariance matrix given by $\sigma^{2}_{\epsilon}C$ in which $C$ is an $n \times n$ matrix of the phylogenetic correlation (PC).

@@

\begin{equation}
Z^{C}_{i} = (BS^{T}_{i}J^{T}_{i} \ast X^{T}_{i})^{T},
\end{equation}

\ml{double check if $l and p$ are the same with lme4}

where $\ast$ is the Khatri-Rao product, $BS_{i}$ is an $l_{i} \times b_{i}$ matrix of species--branch relations; $J_{i}$ the indicator matrix of grouping factors indices matrix size $n \times l_{i}$; $X_{i}$ is the raw random effects model matrix size $n \times p_{i}$.

\ml{double kronecker for interactions}

@@

\begin{tabular}{|c|c|c|}
\hline
Type of RE	& Formula	& Platform	\\
\hline

Single site intercept	  &	1 $\mid$ sp	& gls, lme4 \\
Single site intercept and uncorrelated slopes		&  1 $\mid$ sp + X $\mid$ sp		& lme4 \\
Single site intercept and correlated slopes 			& 1 + X $\mid$ sp					& lme4 \\
\hline
Multiple site intercept 									&  1 $\mid$ sp 						& pez, lme4 \\
Multiple site intercept and uncorrelated slopes 	&  1 $\mid$ sp + X $\mid$ sp 		& pez, lme4 \\
Multiple site intercept and uncorrelated slopes 	& 	1 + X $\mid$ sp					& lme4 \\
ditto with site interaction								& ditto above $\mid$ sp:site		& ditto above \\
\hline
% \vspace{1in}
\end{tabular}

We generate test data using a simple glmm framework that varies in complexity in random effect described in Table 1 \ml{macro this}. All simulations and fits were performed with R.
